---
title: "Assignment-4"
author: "Harkirat"
date: "August 06, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### This task is to is to use R graphics to describe the data. Three seperate datasets are chosen to draw below plots.
* histogram
* boxplot
* scatterplot


#### 1. The first dataset of titanic is used to display one dimensional data of frequency. 

```{r}
#install.packages(c("ggplot2","RCurl"))
library(RCurl)
library(ggplot2)

url1 <- "https://raw.githubusercontent.com/GoHarry/R-Assignment-5/master/Titanic.csv"
titanic <- getURL(url1)
titanic_df <- read.csv(text=titanic,head=TRUE,sep=",")
head(titanic_df)
ggplot(titanic_df, aes(x=Freq)) + geom_histogram(binwidth=100)

```


#### 2. The second dataset of chicken weight is used to display boxplot. Discrete variable feed is used on x axis and weight of chickens are displayed on y axis. This shows clearly that chicken on casein feed have higher weights and chicken on horsebean have lowest weight among other categories. 

```{r}

url2 <- "https://raw.githubusercontent.com/GoHarry/R-Assignment-5/master/chickwts.csv"
chicken_weight <- getURL(url2)
chicken_weight_df <- read.csv(text=chicken_weight,head=TRUE,sep=",")
ggplot(chicken_weight_df, aes(x=feed, y=weight)) + geom_boxplot()

```


#### 3. The third dataset of trees is used to display scatterplot. Continuous variable girth is used on x axis and another continuous variable height of trees is displayed on y axis. This shows clearly that height of trees is somewhat proportional to their girth. 

```{r}

url3 <- "https://raw.githubusercontent.com/GoHarry/R-Assignment-5/master/trees.csv"
trees <- getURL(url3)
trees_df <- read.csv(text=trees,header=T,sep=",",stringsAsFactors = FALSE)
ggplot(trees_df, aes(x=Girth, y=Height)) + geom_point()

```
